---
title: "Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source: embed
---

```{r setup, include=FALSE}
library(flexdashboard)
library(tidyverse)
library(p8105.datasets)
library(plotly)
```

```{r}
data("ny_noaa")

sample_noaa = sample_n(ny_noaa, 500)

noaa_clean = 
  sample_noaa %>% 
  janitor::clean_names() %>% 
  separate(date, into = c("year", "month", "day"), convert = TRUE) %>% 
  mutate(
    tmax = as.numeric(tmax),
    tmin = as.numeric(tmin),
    snow_mm = snow,
    snow = round(snow_mm * 0.03937 * 4) / 4)
  
```

```


Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}
instacart_clean %>% 
  plot_ly(x = ~aisle, y = ~long, 
          color = ~price, text = ~text_label,
          alpha = 0.5, type = "scatter", mode = "markers")
```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}
nyc_airbnb %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  plot_ly(y = ~price, x = ~neighbourhood, color = ~neighbourhood,
          type = "box", colors = "viridis")
```

### Chart C

```{r}
nyc_airbnb %>% 
  count(neighbourhood) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, n)) %>% 
  plot_ly(x = ~neighbourhood, y = ~n, color = ~neighbourhood, type = "bar", colors = "viridis")
```

